### 2017-03-05 README.Rmd
updated autoplot function

#### Classification example

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos).
grid.arrange(
  partial(pima.svm, pred.var = "glucose", plot = TRUE, train = pima),
  partial(pima.svm, pred.var = "age", plot = TRUE, train = pima),
  partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, train = pima),
  ncol = 3
)
```

>>>>

#### Using `autoplot` to produce `ggplot2` graphics

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos).
pd.glucose <- partial(pima.svm, pred.var = "glucose", prob = TRUE, train = pima)
pd.age <- partial(pima.svm, pred.var = "age", prob = TRUE, train = pima)
pd.glucose.age <- partial(pima.svm, pred.var = c("glucose", "age"), prob = TRUE, 
                          train = pima)

# Dislay all three plots together
grid.arrange(
  autoplot(pd.glucose),
  autoplot(pd.age),
  autoplot(pd.glucose.age, contour = TRUE),
  ncol = 3
)
```
